### 2016-08-16 ch01-intro/introduction.tex
Change spacing around headings, epigraphs, ...
Tweak for better pagination
Comments from Johan

\begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
  \caption[System identification loop]{System identification loop. \disclaimer{Adapted from \citep[Figure 1.10]{Ljung1999} and \citep{Mehra1981}.}}
  \label{fig:intro:identification-cycle}
\end{figure}

@@

\paragraph{Select a model structure}
Once an experiment has been performed, the obtained input-output data are to be processed.
In many cases, the eventual goal of identification is to obtain a parametric model, so the user has to select a model structure and complexity based on both his prior knowledge and on the data.
A useful tool to help choose the model structure and/or model orders, is to inspect a nonparametric model of the system.
One such tool is the frequency response function.
For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in terms of  approximate resonance frequencies, asymptotic slopes, \latin{etc.}
This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
However, since most nonparametric estimators enforce very little prior knowledge about the system, it can sometimes be problematic to clearly distinguish noise in the measurements and the actual systematic behavior.

@@

\section{User-Friendly System Identification}
In the previous section, it has been seen that some of the system identification steps require a significant amount of prior knowledge and craftsmanship of the user to make good choices.

@@

\subsection{Contributions}
In this dissertation, we look into a few aspects of the identification workflow with the goal to make the whole process more user-friendly.
Each of these aspects will be dealt with in its own chapter.

@@

\subsection{Outline and Publications}
   The lion's share of this thesis has been published in either peer-reviewed  journals or conferences.
   This section links my different publications to the different sections in this thesis.
   For an overview of publications grouped by type, please refer to page~\pageref{publicationList}.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
  \caption[System identification loop]{System identification loop. \disclaimer{{\footnotesize Adapted from \citep[Figure 1.10]{Ljung1999} and \citep{Mehra1981}.}}}
  \label{fig:intro:identification-cycle}
\end{figure}

@@

\paragraph{Select a model structure}
Once an experiment has been performed, the obtained input-output data are to be processed.
In many cases, the eventual goal of identification is to obtain a parametric model, so the user has to select a model structure and complexity based on both his prior knowledge and on the data.
A useful tool to help choose the model structure and/or model orders, is to inspect a nonparametric model of the system.
One such tool is the frequency response function.
For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in terms of  approximate resonance frequencies, asymptotic slopes, \latin{etc.}
This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
However, since most nonparametric estimators enforce very little prior knowledge about the system, it can sometimes be problematic to clearly distinguish noise in the measurements from the actual systematic behavior.

@@

\newpage
\section{User-Friendly System Identification}
In the previous section, it has been seen that some of the system identification steps require a significant amount of prior knowledge and craftsmanship of the user to make good choices.

@@

\newpage
\subsection{Contributions}
In this dissertation, we look into a few aspects of the identification workflow with the goal to make the whole process more user-friendly.
Each of these aspects will be dealt with in its own chapter.

@@

\newpage
\subsection{Outline and Publications}
   The lion's share of this thesis has been published in either peer-reviewed  journals or conferences.
   This section links my different publications to the different sections in this thesis.
   For an overview of publications grouped by type, please refer to page~\pageref{publicationList}.

### 2016-08-16 ch02-qlogms/excitation-design.tex
Comments from Johan

\section{Input Design}
\label{sec:excitation:inputDesign}
For the theoretical analysis, we consider \gls{SISO} \gls{OE} systems, i.e.
\begin{align}
y(t) &=G(s,\theta)u(t)  + H(s,\vartheta)e(t),
\end{align}
where $u(t)$ is a known input sequence, $y(t)$ the output sequence, and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
$G$ and $H$ are rational, time-invariant transfer function in continuous time.
For notational simplicity, $s$ is used both as the complex Laplace variable and the differentiation operator; it should be clear from the context which is used. 
The transfer function is parameterized by the vector $\theta$.
These parameters are unknown and hence we are interested in estimating their values.
\begin{assumption}
The noise filter $H(s,\vartheta)$ is assumed to be independently parametrized from the plant $G(s,\theta)$, i.e. $\vartheta$ and $\theta$ are independent.
\end{assumption}
\begin{assumption}
For the derivations, $H(s,\vartheta) = 1$ is used as a working assumption such that the disturbing noise on the output is zero mean Gaussian white noise.
When this assumption is violated, one has to first measure the noise coloring and use this knowledge to predistort the input to account for the noise coloring.
\end{assumption}

@@

   The free parameters $(\dc, \damping, \wn, \wz)$ of the sub-system are reduced to only $(\damping, \wn)$ and the others are fixed during our experiments: $\dc = 1$ and $\wz \to \infty$. 
   \begin{remark}
   Implicitly, this considers a design where each of the sub-systems have an equal gain $\dc=1$ and residue $\wz \to\infty$.
   In practice, this is often not a reasonable assumption, but the design can be adapted in a straightforward manner.
   Concretely, using a first experiment with the proposed signal, one can estimate the different gains of the sub-systems and optimize the amplitude spectrum of the signal to take those into account: for sub-systems where $\dc$ is lower than on average, the amplitude spectrum needs to be increased near the resonance frequency and \latin{vice versa}.
   \end{remark}

>>>>

\section{Input Design}
\label{sec:excitation:inputDesign}
For the theoretical analysis, we consider \gls{SISO} \gls{OE} systems, i.e.
\begin{align}
y(t) &=G(s,\theta)u(t)  + H(s,\vartheta)e(t),
\end{align}
where $u(t)$ is a known input sequence, $y(t)$ the output sequence, and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
$G$ and $H$ are rational, time-invariant transfer function in continuous time.
For notational simplicity, $s$ is used both as the complex Laplace variable and the differentiation operator; it should be clear from the context which is used. 
The transfer function is parameterized by the vector $\theta$.
These parameters are unknown and hence we are interested in estimating their values.
\begin{assumption}
The noise filter $H(s,\vartheta)$ is assumed to be independently parametrized from the plant $G(s,\theta)$.
\end{assumption}
\begin{assumption}
For the derivations, $H(s,\vartheta) = 1$ is used as a working assumption such that the disturbing noise on the output is zero mean Gaussian white noise.
When this assumption is violated, one has to first measure the noise coloring and use this knowledge to predistort the input to account for the noise coloring.
\end{assumption}

@@

   The free parameters $(\dc, \damping, \wn, \wz)$ of the sub-system are reduced to only $(\damping, \wn)$ and the others are fixed during our experiments: $\dc = 1$ and $\wz \to \infty$. 
   \begin{remark}
   Implicitly, this considers a design where each of the sub-systems have an equal gain $\dc=1$ and residue $\wz \to\infty$.
   In practice, this is often not a reasonable assumption, but the design can be adapted in a straightforward manner.
   Concretely, using a first experiment with the proposed signal, one can estimate the different gains of the sub-systems and optimize the amplitude spectrum of the signal to take those into account: for sub-systems where $\dc$ is lower than on average, the amplitude spectrum needs to be increased near the resonance frequency and \latin{vice versa} if the uncertainty of the parameters is required to be constant.
   Of course, the appropriate actions to compensate for differing $\dc=1$ depend on the actual goal of the model.
   \end{remark}

### 2016-08-16 ch03-lrm/leakage.tex
Comments from Johan

\disclaimer{
This appendix is based on multiple expositions regarding transient contributions in the frequency domain.
For a more in-depth discussion, we refer to \citep{Pintelon1997ARB}, \citep{Pintelon1997Transient}, \citep{Schoukens1999}, \citep[Section 2]{McKelvey2012LRM}, and \citep[Sections 2.6.3, 6.3.2 and Appendix 6.B]{Pintelon2012}.
}

This appendix derives the transient contributions in the frequency domain when a \gls{LTI} system is observed during a finite measurement window (i.e. $t \in {0, \ldots, N-1}$) using the same approach as in \citet[Appendix 6.B]{Pintelon2012}.

>>>>

\disclaimer{
This appendix is based on multiple expositions regarding transient contributions in the frequency domain.
For a more in-depth discussion, we refer to \citep{Pintelon1997ARB}, \citep{Pintelon1997Transient}, \citep{Schoukens1999}, \citep{McKelvey2002}, \citep[Section 2]{McKelvey2012LRM}, and \citep[Sections 2.6.3, 6.3.2 and Appendix 6.B]{Pintelon2012}.
}

This appendix derives the transient contributions in the frequency domain when a \gls{LTI} system is observed during a finite measurement window (i.e. $t \in {0, \ldots, N-1}$).
The following derivations are repeated from \citep[Appending 6.B]{Pintelon2012}, but have been adapted in notation.

### 2016-08-16 ch05-initvals/initial-values.tex
Comments from Johan

The success rate $\successRate_{\bullet}$ of an initialization scheme $\bullet$ is defined as the probability that it reaches the \emph{best local optimum}, i.e.
\begin{equation}
\successRate_{\bullet} = 
  \Prob{  \model{\bullet} \approx \model{\true{}}  }
\text{.}
\end{equation}
In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is implemented practically as
\begin{equation}\label{eq:successrateTol}
\successRate_{\bullet} \isdef \Prob{ \norm[2]{\model{\bullet} - \model{\true{}}} < \absoluteTolerance}
\end{equation}
with $\absoluteTolerance$ a numerical tolerance that will be specified later on.

>>>>

The success rate $\successRate_{\bullet}$ of an initialization scheme $\bullet$ is defined as the probability that it reaches the \emph{best local optimum}.
In practice, and since the iterative algorithm usually does not reach the local optimum precisely, this is implemented practically as
\begin{equation}\label{eq:successrateTol}
\successRate_{\bullet} \isdef \Prob{ \norm[2]{\model{\bullet} - \model{\true{}}} < \absoluteTolerance}
\end{equation}
with $\absoluteTolerance$ a numerical tolerance that will be specified later on.

### 2016-08-16 ch06-concl/conclusions.tex
Comments from Johan

    Specifically for the \gls{LRM}, currently a model structure that is equivalent to rational forms in continuous time, i.e. the (local) transfer function model is isomorphic with
    \begin{equation}
      \LocalModel[\CT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \dW^{i}}{\Sum_i  a_i \dW^{i}}
    \end{equation}
    There have already been some experiments with other model structures such as local discrete time models where
    \begin{equation}
      \LocalModel[\DT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \exp (ji\dW\Ts)}{\Sum_i  a_i \exp (ji\dW\Ts) }
    \end{equation}
    but these have proven more difficult to estimate numerically and hence unreliable~\citep[Section 2.4]{Pintelon2006BJ1}.
    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} with complex coefficients.
    The \gls{LRM} (and hence also \gls{LPM}) could be extended to other model structures that are fine-tuned for specific applications as is also sometimes done for fully parametric system identification in the frequency domain~\citep[p. 179]{Pintelon2012}.
    E.g. in electrochemistry it is common~\citep{Wang1987} to describe diffusion phenomena using Warburg impedances which are proportional to $\sqrt{s}$ (with $s$ the Laplace variable).
    On the other hand, in microwave engineering~\citep{Rizzi1988,Pozar2005}, commensurate filters are easily described using Richard's variable $R=\tanh (\tau s)$ with $\tau$ the delay of the considered transmission lines.
    For these altered models, however, it should be verified whether numerical conditioning becomes a similar nuisance as for discrete-time models.

>>>>

    Specifically for the \gls{LRM}, currently a model structure that is equivalent to rational forms in continuous time, i.e. the (local) transfer function model is isomorphic with
    \begin{equation}
      \LocalModel[\CT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \dW^{i}}{\Sum_i  a_i \dW^{i}}
    \end{equation}
    There have already been some experiments with other model structures such as local discrete time models where
    \begin{equation}
      \LocalModel[\DT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \exp (ji\dW\Ts)}{\Sum_i  a_i \exp (ji\dW\Ts) }
    \end{equation}
    but these have proven more difficult to estimate numerically and hence unreliable~\citep[Section 2.4]{Pintelon2006BJ1}.
    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} with complex coefficients.
    The \gls{LRM} (and hence also \gls{LPM}) could be extended to other model structures that are fine-tuned for specific applications as is also sometimes done for fully parametric system identification in the frequency domain~\citep[p. 179]{Pintelon2012}.
    E.g. in electrochemistry it is common~\citep{Wang1987} to describe diffusion phenomena using Warburg impedances which are proportional to $\sqrt{s}$ (with $s$ the Laplace variable).
    In such diffusion problems, it can be shown~\citep[p. 181]{Pintelon2012} that the system transients dampen as an $\bigO{t^{3/2}}$, which is considerable slower than for lumped continuous-time systems and discrete-time where the impulse decays as an $\bigO{e^{0t}}$.
As a result, estimating diffusion transients is an even more important task than the setting discussed in this dissertation.
    On the other hand, in microwave engineering~\citep{Rizzi1988,Pozar2005}, commensurate filters are easily described using Richard's variable $R=\tanh (\tau s)$ with $\tau$ the delay of the considered transmission lines.
    For these altered models, however, it should be verified whether numerical conditioning becomes a similar nuisance as for discrete-time models.
